The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-16 src/ms.tex
minor edits to new AAT section

>>>>

\subsubsection{Data Central and the Anglo-Australian Telescope Archive}
% \secauthor{James Tocknell}
Data Central is one of the five Australian Virtual Observatory\footnote{known as
  the All-Sky Virtual Observatory, or ASVO} nodes, providing both Australian and
international astronomers access to and services for surveys of the southern
sky. Whilst primarily hosting optical data, including the Anglo-Australian
Telescope (AAT) Archive\footnote{The AAT Archive is currently jointly managed by
  Data Central, Astronomy Australia Limited (AAL), and National Computational
  Infrastructure (NCI)}, Data Central also assists theoretical and radio
astronomers host and manage their data.

\python is widely used by Data Central, and \astropy and its wider ecosystem
play a vital role in the initial ingestion, reduction, access and visualization
of the hosted data and services. For example, the AAT Archive hosts data back to
1974, so \astropycoordinates, \astropytime and \astropyfits are used to ingest
data flowing from the AAT to ensure that a consistent time and coordinate system
is provided to users for simpler querying.

As many of the surveys hosted by Data Central are spectroscopic surveys from the
AAT, \package{specutils} is heavily used to standardize the variety of encodings
of spectroscopic data into a form easily readable and visualizable by many
standard tools (such as \package{ds9} or \package{splat}). Data Central has
upstreamed into \package{specutils} loaders for all hosted spectra, including
2dfdr-reduced spectra from the AAT Archive, and strongly encourages other
archives to provide loaders for their data to further reuse of existing archival
data.
